Review questions list

### 2020-10-14 docs/revision/reply.tex
update: fixed-typos:: update-first-argument

\documentclass{article}
\usepackage[utf8]{inputenc}

@@

	During our initial studies, we have studied the effect of the network architecture on the accuracy. During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve. Specifically, in SPR dataset, this requirement is evident. Higher number of layers increases the required number of samples to train causing further problems. Similar situation exists for the number of neurons. However, it is possible that there might be a better combination of layers and neurons as we have not performed any exhaustive optimization on the neural network.

@@

	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations. The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems. We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the this more difficult problem. In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases. The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit. In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{color,soul}

@@

	During our initial \hl{systematic experiments; instead of "studies"}, we have studied the effect of the network architecture on the accuracy. During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve. Specifically, in SPR dataset, this requirement is evident. Higher number of layers \hl{not only potentially leads to overfitting, but also to an  increase in} the required number of samples to train causing further problems. Similar situation exists for the number of neurons. However, it is possible that there might be a better combination of layers and neurons as we have not performed any exhaustive optimization on the neural network.

@@

	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations. The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems. We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the more difficult problem. In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases. The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit. In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.
